Implementation of Concurrent Hash Tables in Java

### 2022-04-29 paper.tex
paper

>>>>

Follow up work:

In the future, we might follow up this research by including other types of hash sets and performing more varied testing. It would be interesting to consider a lock-free tables, such as the lock-free hash set from The Art of Multiprocessor Programming. That table would likely have very different performance characteristics, given it's lock-free nature and unique overhead of maintaining a linked-list and buckets. 
We could also expand our testing to include different percentages of insertions, deletions, and reads. This might reveal other differences in performance.
